SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-06 docs/questioning.tex
work on the analysis section

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks.
\end{IEEEkeywords}

@@

There is already a survey on mitigating software vulnerabilities
in general~\cite{SZ12}. The scope of that
research is pretty wide and leaves out the majority of the
approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned in the previous paragraph.

@@

In this section we categorize and describe the various mechanisms
developed to detect the attacks described earlier in
Section~\ref{sec:attacks}. We accompany our descriptions
with comments related to the following dimensions:
a) diagnostic performance, b) security, c) ease of use
and d) detection locus. Regarding the other two
dimensions we provide general remarks in our upcoming
``Analysis" section (\ref{sec:analysis}).

@@

@@

@@

\subsection{Trade-offs}

>>>>

\begin{IEEEkeywords}
Security and Protection, Application Security, Code injection Attacks,
Testing, Cross-Site Scripting.
\end{IEEEkeywords}

@@

There is already a survey on mitigating software vulnerabilities
in general~\cite{SZ12}. The scope of that
research is pretty wide and leaves out the majority of the
approaches and mechanisms that we report here.
This is mainly because this work includes countermeasures
that detect such vulnerabilities via program analysis
(which is done during development or testing), while
we include protection mechanisms that counter
such attacks when they take place.
Also, countermeasures that prevent {\sc sql}
injection attacks~\cite{HVO06}, have already been surveyed.
However, this survey is quite old and since then
the number of countermeasures that detect {\sc sql}
injection attacks alone, has been drastically increased
as we mentioned earlier.

@@

In this section we categorize and describe the various mechanisms
developed to detect the attacks described in
Section~\ref{sec:attacks}. We accompany our descriptions
with comments related to the following dimensions:
a) diagnostic performance, b) security, c) ease of use
and d) detection locus. Regarding the other two
dimensions we provide general remarks in our upcoming
``Analysis" section (\ref{sec:analysis}).

@@

\subsubsection{Diagnostic Performance}

@@

\subsubsection{Computational Performance}

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
on the server-side, all the mechanisms that detect
such attacks are placed in some point within the server.

However, in this case of mechanisms that deal
with JavaScript-driven {\sc xss} attacks
we observe that attack detection may take place
either on the server-side or on the client-side.

@@
